Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
fix test-DataPipeline

As COVID-19 is also an ongoing epidemic, more data surfaces and updates on a continuous basis. Future research directions consist of updating the dataset by extending the time range to include newer data and including additional countries and cities - such as by looking at the climate and infection data in American and Canadian cities. In particular, by looking at the results of other cities and making a comparison with the results in Italy, we can observe if the linear assumption between seasonal factors and R holds true across different climate regions. If not, we can try fitting while assuming a nonlinear relationship between R and seasonal factors. Additional future research includes looking into statistical simulation models which consider intercity travel and geographic proximity. Using the results from the simulation models, we can help further isolate the direct effects of temperature and humidity on the reproduction rate of COVID-19.

- Looking at the climate and infection data in American and Canadian cities as the situation develops further. In particular, compare this with the results in Italy, and observe if the linear assumption between seasonal factors and $R$ holds true across different climate regions. If not, try fitting while assuming a nonlinear relationship between $R$ and seasonal factors.
- Look into statistical simulation models which consider intercity travel and geographic proximity.

>>>>

One particularly counterintuitive result in de

With our `cfc19i` library, it is

Looking at the climate and infection data in American and Canadian cities as the situation develops further. In particular, compare this with the results in Italy, and observe if the linear assumption between seasonal factors and $R$ holds true across different climate regions. If not, try fitting while assuming a nonlinear relationship between $R$ and seasonal factors.

Look into statistical simulation models which consider intercity travel and geographic proximity.
